---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Support.CCA

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/nilanjanalaha/Support.CCA.svg?branch=master)](https://travis-ci.org/nilanjanalaha/Support.CCA)
<!-- badges: end -->

 Support.CCA estimates the support of canonical directions using the methods developed in Laha and Mukherjee (2020).

## Installation

Install  from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nilanjanalaha/Support.CCA")
```
## Example

We will generate a toy dataset. First let us generate $\alpha$ and $\beta$. 

```{r example}
library(mvtnorm)
#Simulate  standard normal data matrix: first generate alpha and beta
p <- 500; q <- 200; al <- rep(0, p); be <- rep(0,q)
al[1:5] <- 1
be[20:25] <- 1

#Standardize alpha and beta
al <- al/sqrt(sum(al^2))
be <- be/sqrt(sum(be^2))
n <- 800; rho <- 0.5

```

Note that the support of $\alpha$ and $\beta$ are
\[\text{Sup}(\alpha)=\{1,\ldots,5\},\quad \text{Sup}(\beta)=\{20,\ldots,25\}.\]

Now we will generate two gaussian data matrices X and Y with rank one covariance matrix, and canonical
covariates are $\alpha$ and $\beta$.
```{r example: continued}

#Creating the  covariance matrix
Sigma_mat <- function(p,q,al,be, rho)
{
  Sx <- diag(rep(1,p), p, p)
  Sy <- diag(rep(1,q), q, q)
  Sxy <- tcrossprod(crossprod(rho*Sx, outer(al, be)), Sy)
  Syx <- t(Sxy)
  rbind(cbind(Sx, Sxy), cbind(Syx, Sy))
}
truesigma <-  Sigma_mat(p,q,al,be, rho)

#Simulating the data
set.seed(4)
Z <- mvtnorm::rmvnorm(n, sigma = truesigma)
x <- Z[,1:p]
y <- Z[,(p+1):(p+q)]
```



The function c_support provides supports of the leading pair of canonical covariates $\alpha$ and $\beta$. It uses a coordinate thresholding algorithm (Laha and Mukherjee., 2020).

```{r cars}
library(Support.CCA)
temp <- c_support(x,y)$sup.x

#Proportion of recovered support
length(which(temp[1:5]==1))/5

#recovered support
which(temp==1)
```

We see a lot of elements which are not actually in the support, are estimated as part of the support.
If we  put regularization on the number of non-zero elements (sparsity) of 
$\alpha$ and $\beta$, c_support will yield better estimates of the supports. We will use 7 as an estimator of the sparsities, and pass it as the parameter sv=c(7, 7).

```{r better}
Sx <- diag(rep(1,p))
Sy <- diag(rep(1,q))
temp <- c_support(x,y, sv=c(7, 7))$sup.x

#Proportion of recovered support
length(which(temp[1:5]==1))/5

#estimated support
which(temp==1)
```

Thus, we see providing a regulrization parameter facilitates sparser support recovery.
However, c_support has asymptotic garuantees only if  the covariance matrices are also provided. Still, as we see, c_support includes some elements, which are not in the support of $\alpha$, to be in the support.

```{r better yet}
Sx <- diag(rep(1,p))
Sy <- diag(rep(1,q))
temp <- c_support(x,y, sv=c(7, 7), Sx=Sx, Sy=Sy)$sup.x

#Proportion of recovered support
length(which(temp[1:5]==1))/5

#Esimated support
which(temp==1)
```

The other method g_support also estimates the support of $\alpha$ and $\beta$. 
```{r cars 3}
temp <- g_support(x,y)$sup.x

#Proportion of recovered support
length(which(temp[1:5]==1))/5

```

We see that g_support recovers 80$\%$ of the data. Now we will see which elements are in estimated support.
```{r cars 31}
#Estimated support 
which(temp==1)

```

We see that for this dataset, g_support does not include any element which is not in the support. 

 One can pass a tuning parameter Cg to g_support. Cg  controls the length of the estimated support. If we increase Cg, then the estimated support shrinks. A smaller Cg results in an estimated support with more zeros. The default value is 0.50. See the documentation typing`` ?g.support" in the console for more details.
  
```{r cars 2}
temp <- g_support(x,y, Cg=.4)$sup.x

#Proportion of recovered support
length(which(temp[1:5]==1))/5

#Estimated support 
which(temp==1)
```

We see that Cg=0.40 leads to exact support recovery of $\alpha$.
One can also specify Sx and Sy in g_support, the variances of X and Y,  but it is not necessary.

```{r cars 4}
temp <- g_support(x,y, Cg=.4, Sx=Sx, Sy=Sy)$sup.x

#Proportion of recovered support
length(which(temp[1:5]==1))/5

#Estimated support 
which(temp==1)
```


